---
title: "CARE secondary parotid tumours"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    code_folding: hide
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
pacman::p_load(tidyverse, 
               gtsummary,
               ggcharts , # see https://thomas-neitmann.github.io/ggcharts/reference/dumbbell_chart.html
               dlookr, 
               scales, # for the % scales in ggplot2
               patchwork, # for multiple plots
               santoku, # to break variables
               DescTools, # for agreement
               irr, # for agreement
               janitor)
```

For wordcloud

```{r}
pacman::p_load(wordcloud, # word-cloud generator 
               SnowballC, # for text stemming
               RColorBrewer, # palette
               wordcloud2, 
               tm) # for text mining
```

```{r}
theme_set(theme_minimal())
```

# Dataset

```{r}
df <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRKPzFe2lbF87DNe9SBjuaIb5iMb4nCmgvfdyT4v-NjK-BZBR-HkUIUdgiML3t30EqQ1RCep0sExatK/pub?output=csv")
```

```{r}
names(df)
```

For the wordcloud later

```{r}
text <- df$`Copy and paste the abstract`
```

```{r}
dlookr::diagnose(df)
```

```{r}
df <- df %>%
  mutate(JOURNAL = str_to_title(JOURNAL)) %>% # change the capitalization
  mutate(JOURNAL = str_trim(JOURNAL, side = c("both"))) %>% # remove spaces
  mutate(JOURNAL = str_replace(JOURNAL, "Resaerch", "Research"))  %>% 
  mutate(JOURNAL = str_replace(JOURNAL, "Otolaryngology-Head And Neck Surgery", "Otolaryngology–Head And Neck Surgery")) %>% 
  mutate(JOURNAL = str_replace(JOURNAL, "Otolaryngology–Head And Neck Surgery", "Archives Of Otolaryngology--Head & Neck Surgery")) %>%
  mutate(JOURNAL = str_replace(JOURNAL, "The Journal Of Laryngology & Otology", "The Journal Of Laryngology And Otology"))
```

# Check agreement

How many raters?

```{r}
df %>% 
  tabyl(Reviewer)
```

## Kappa

```{r}
df %>% 
  select(Reviewer, ID,  `CARE Appraisal [Abstract 3b Main symptoms and/or important clinical findings]`:`CARE Appraisal [Key Words 2 2 to 5 key words that identify diagnoses or interventions in this case report, including "case report"]`) %>% # leave only the relevant columns
  filter(Reviewer != "SU") %>%  # remove SU from the rater 
  
  # now reshape the dataset to obtain three columns
  pivot_longer(-c(Reviewer, ID), 
               names_to = "Care_item", 
               values_to = "Care_values") %>% 
  select(-c(Care_item)) %>% 
  
  # now reshape again to obtains the values per rater
  pivot_wider(id_cols = ID, 
              names_from = Reviewer, 
              values_from = Care_values) %>% 
  tidyr::unnest() %>%  # this is to recover the values, check shorturl.at/gpAG3 
  filter(!is.na(IA)) %>% 
  filter(!is.na(PJ)) %>% 
  select(-ID) %>% 
  kappam.fleiss(., detail=TRUE)
```

**The kappa between the rater is .715**

Since they are comparable, I will leave only one + SU

```{r}
df <- df %>% 
  filter(Reviewer %in% c('IA', 'SU'))
```

## add a continent column

```{r}
countries <- read_csv("https://raw.githubusercontent.com/dbouquin/IS_608/master/NanosatDB_munging/Countries-Continents.csv")
glimpse(countries)
```

```{r}
df <- df %>% 
  mutate(`Country of the correspondence author` = (str_replace_all(`Country of the correspondence author`, "United States", "US"))) %>% 
left_join(., countries, by = c("Country of the correspondence author" = "Country")) %>%
  mutate(Continent = case_when(
    `Country of the correspondence author` == "Taiwan" ~ "Asia", 
    `Country of the correspondence author` == "Australia" ~ "Oceania",
    `Country of the correspondence author` == "Canada" ~ "North America",
    `Country of the correspondence author` == "China" ~ "Asia",
    `Country of the correspondence author` == "India" ~ "Asia",
    `Country of the correspondence author` == "Japan" ~ "Asia",
    `Country of the correspondence author` == "Israel" ~ "Asia",
    `Country of the correspondence author` == "Kuwait" ~ "Asia",
    `Country of the correspondence author` == "Morocco" ~ "Africa",
    `Country of the correspondence author` == "Qatar" ~ "Asia",
    `Country of the correspondence author` == "Tunisia" ~ "Africa",
    TRUE ~ "Europe"
  )) 
```

```{r}
rm(countries)
```

# EDA

### How many papers

```{r}
n_distinct(df$TITLE)
```

### From how many journals?

```{r}
n_distinct(df$JOURNAL)
```

### List of journals with at least 3 articles

```{r}
df %>% 
  mutate(JOURNAL = fct_lump_min(JOURNAL, min = 3)) %>% 
  count(JOURNAL) %>% 
  arrange(desc(n))
```

### Patients distribution by paper

```{r}
df %>% 
  ggplot(aes(x = `Number of patients`)) + 
  geom_histogram(bins = 6)
```

### How many patients per paper

```{r}
summary(df$`Number of patients`)
```

### How many patients in total

```{r}
sum(df$`Number of patients`)
```

### Males and females

```{r}
df %>% 
  pivot_longer(`Males reported`:`Females reported`, 
               names_to = "sex", 
               values_to = "sex_values") %>% 
  ggplot(aes(x = sex_values, 
             fill = "sex")) + 
               
  geom_histogram(bins = 6) + 
  facet_grid(sex ~ .) + 
  theme(legend.position="none")
```

### Year of publication

```{r}
df %>% 
  ggplot(aes(x = `YEAR published`)) + 
  geom_histogram(bins = 10)
```

```{r}
df %>% 
  mutate(Continent = fct_lump_min(Continent, min = 10)) %>% 
  ggplot(aes(x = `YEAR published`, 
             fill = Continent)) + 
  geom_histogram(bins = 10) + 
  facet_grid(Continent ~ . )
```

### Age of the patients

```{r}
df %>% 
  ggplot(aes(Age)) + 
  geom_histogram(bins = 10)
```

```{r}
df %>%   
  mutate(Continent = fct_lump_min(Continent, min = 10)) %>% 
  ggplot(aes(x = Age, 
             fill = Continent)) + 
  geom_histogram(bins = 10) + 
  facet_grid(Continent ~ . )
```

### Age of the patients by sex

```{r}
df %>% 
  pivot_longer(`Males reported`:`Females reported`, 
               names_to = "sex", 
               values_to = "sex_values") %>% 
  ggplot(aes(y = sex_values, 
             x = Age, 
             color = sex)) + 
  geom_jitter(alpha = .7) + 
  facet_grid(sex ~ . ) +
  theme(legend.position="none")
```

```{r}
df %>% 
  pivot_longer(`Males reported`:`Females reported`, 
               names_to = "sex", 
               values_to = "sex_values") %>% 
  ggplot(aes(y = Age, 
             x = sex, 
             color = sex)) + 
  geom_boxplot(alpha = .7) + 
  geom_jitter(alpha = .2, width = .2) +
  theme(legend.position="none")
```

### Age by Continent

```{r}
df %>% 
  distinct_at(vars(ID), .keep_all = TRUE) %>% # filter unique values
  ggplot(aes(x = fct_reorder(Continent, Age, .fun = median), 
             y = Age)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .1, width = 0.2)
```

### Case reports by continent

```{r}
df %>% 
  distinct_at(vars(ID), .keep_all = TRUE) %>% # filter unique values
  group_by(Continent, `YEAR published`) %>% 
  ggplot(aes(x = `YEAR published`, 
             y = `Number of patients`, 
             color = Continent))  +
  geom_jitter(alpha = .4) + 
  scale_y_log10() + 
  facet_grid(. ~ Continent)
```

# CARE ANALYSIS

Convert the answers to points

Yes = 1

Unclear = .1

No = 0

```{r}
df <- df %>% 
  select(-c(TITLE, Reviewer, `Laika zīmogs`, 
            AUTHORS, `Copy and paste the abstract`, 
            Comments)) %>% 
  # reshape the dataset
  pivot_longer(contains("CARE"), 
               names_to = "CARE_item", 
               values_to = "CARE_value") %>% 
  # create a new column with the values of CARE
  mutate(CARE_value_num = case_when(
    CARE_value == "Yes" ~ "1", 
    CARE_value == "Unclear" ~ "0.1", 
    TRUE ~ "0"
  ))
```

## TABLE 1 CARE items compliance

Compliance per CARE item

```{r}
df %>% 
  select(CARE_item, CARE_value) %>% 
  mutate(CARE_item = fct_inorder(CARE_item)) %>% # reorder by appeareance
  gtsummary::tbl_summary(by = CARE_value, 
                         percent = "row") %>% 
  modify_header(update = list(
  label ~ '**Characteristic**',
  stat_1 ~ '**No**',
  stat_2 ~ '**Unclear**',
  stat_3 ~ '**Yes**'
))
```

Calculate the average quality per paper

```{r}
df_sum <- df %>%
  janitor::clean_names() %>% # convert the names
  mutate(care_value_num = as.double(care_value_num)) %>%  # change from chr to int
  select(id, care_item, care_value_num) %>% # select only some columns. Later need to join
  # reshapre the dataset
  pivot_wider(names_from = "care_item",
              values_from = "care_value_num") %>%
  relocate(id, .after = last_col()) %>% 
  rowwise() %>% 
  mutate(care_sum = sum(c_across(starts_with("care"))), .keep = "all") %>% 
  ungroup() %>% 
  select(ID = id, care_sum)
  
  
```

Now merge the df_sum

```{r}
df <- left_join(df, df_sum, by = "ID")
```

Convert the CARE_num_vale to num

```{r}
df <- df %>% 
  mutate(CARE_value_num = as.double(CARE_value_num))
```

Remove the df_sum

```{r}
rm(df_sum)
```

## FIGURE 4 CARE score by year

Calculate the average quality per year

```{r}
df %>%
  # reshape
  mutate(Decade = floor(`YEAR published` / 10) * 10) %>%
  # mutate(Decade = santoku::chop(`YEAR published`, c(1969, 1979, 1989, 1999, 2009, 2019))) %>%
  pivot_wider(names_from = CARE_item,
              values_from = CARE_value) %>%
  distinct(., ID, .keep_all = TRUE) %>%  # filter unique IDs
  select(ID, Decade, care_sum) %>%
  ggplot(aes(x = as.factor(Decade),
             y = care_sum)) +
  geom_jitter(color = "grey90") +
  geom_boxplot(width = .2, color = "grey60") +
  geom_violin(width = .9, fill = NA) +
  labs(
    title = "Average CARE compliance per decade",
    subtitle = "Median and 25%−75% Quartiles\nDotted line in 2013 marks the publication of the CARE guidelines",
    y = "CARE Compliance",
    x = "Decade"
  ) +
  geom_vline(
    aes(xintercept = 5.3), linetype = "dashed", colour = "red", size = 0.5)
```

### Quality by continent

```{r}
df %>%
  distinct_at(vars(ID), .keep_all = TRUE) %>% # filter unique values, since there is the care_sum for each id 
  ggplot(aes(x = fct_reorder(Continent, care_sum), 
             y = care_sum)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .1) + 
  labs(title = "CARE Compliance by Continent", 
       x = "Continent", 
       y = "CARE score")
  
```

But keep in mind the n for each continent

```{r}
df %>%
  distinct_at(vars(ID), .keep_all = TRUE) %>% # filter unique values, since there is the care_sum for each id 
  group_by(Continent) %>% 
  summarise(n = n(), "Mean" = mean(care_sum), "sd" = sd(care_sum), min = min(care_sum), max = max(care_sum)) %>% 
  mutate_if(is.numeric, round, 1)
```

### Papers published by Year

```{r}
df %>%

  distinct(., ID, .keep_all = TRUE) %>%   # filter unique IDs
  ggplot(aes(x = `YEAR published`)) + 
  geom_histogram(bins = 10, fill = "grey50") + 
  labs(title = "Case reports publishes by year", 
       x = "Year", 
       y = "Articles")
  
```

### papers publishes by year by continent

```{r}
df %>%
  distinct(., ID, .keep_all = TRUE) %>%   # filter unique IDs
  ggplot(aes(x = `YEAR published`, 
             fill = Continent)) +
  geom_histogram(bins = 8) +
  facet_grid(Continent ~  .) +
  labs(title = "Publications by Corresponding Author Country",
       x = "Year",
       y = "Publications") +
  theme(legend.position="none")
```

## create a new CARE simplified name items

```{r}
df <- df %>% 
  mutate(CARE_name_simple = case_when(
    str_detect(CARE_item,"Title 1 The diagnosis")  ~ "01 Title", 
    str_detect(CARE_item,"Key Words 2 2 to 5 key") ~ "02 Keywords",
    str_detect(CARE_item,"Abstract 3") ~ "03 Abstract", 
    str_detect(CARE_item,"Introduction 4") ~ "04 Introduction",
    str_detect(CARE_item,"5") ~ "05 Patient Information",
    str_detect(CARE_item,"6") ~ "06 Clinical Findings",
    str_detect(CARE_item,"7") ~ "07 Timeline",
    str_detect(CARE_item,"8") ~ "08 Diagnostic Assessment",
    str_detect(CARE_item,"9") ~ "09 Therapeutic Intervention",
    str_detect(CARE_item,"10") ~ "10 Follow-up and Outcomes",
    str_detect(CARE_item,"11") ~ "11 Discussion",
    str_detect(CARE_item,"12") ~ "12 Patient Perspective",
    TRUE ~ "13 Informed Consent"
  )) 
```

## Count CARE new items

```{r}
df %>% 
  mutate(CARE_value = fct_relevel(CARE_value, "Yes", "Unclear")) %>%
  select(CARE_name_simple, CARE_value) %>% 
  group_by(CARE_name_simple, CARE_value) %>% 
  # count() %>% 
  gtsummary::tbl_summary(by = CARE_value, 
                         percent = "row") %>% 
  modify_header(update = list(
  label ~ '**Characteristic**',
  stat_1 ~ '**Yes**',
  stat_2 ~ '**Unclear**',
  stat_3 ~ '**No**'
))
```

# Analysis before and after 2013

Create a new var indicating if before or after

```{r}
df <- df %>% 
  mutate(moment = case_when(
    `YEAR published` < 2013 ~ "Before", 
    TRUE ~"After"
  )) 
```

## Table 3

Now compare before and after

```{r}
df %>% 
  mutate(Continent = fct_relevel(Continent, "Europe")) %>% # since europe is the main continent, I will left as baseline
  mutate(moment = fct_relevel(moment, "Before")) %>% # before is the baseline
  distinct_at(vars(ID), .keep_all = TRUE) %>% # filter unique values
  mutate(Continent = fct_lump_min(Continent, min = 3)) %>%  # since there are soo few papers in others continents, Let's lump them
  mutate(JOURNAL = fct_lump_min(JOURNAL, min = 3)) %>% 
  mutate(JOURNAL = fct_relevel(JOURNAL, "Other")) %>% 
  rename("Moment" = "moment") %>% 
  with(lm(care_sum ~ Moment + JOURNAL + Continent)) %>% 
  gtsummary::tbl_regression() %>% 
  gtsummary::add_n(location = "level") %>% 
  gtsummary::bold_labels()

```

## Analysis per item before/after

```{r}
df %>% 
  pivot_wider(names_from = CARE_item, 
              values_from = CARE_value) %>% 
  distinct_at(vars(ID), .keep_all = TRUE) %>%  # filter unique values
  group_by(ID, moment) %>% 
  group_by(moment) %>% 
  summarise(n = n(), mean = mean(care_sum), sd = sd(care_sum)) %>% 
  mutate_if(is.numeric, round, 1)
```

## Main table CARE compliance

```{r}
df %>% 
  # reorder the CARE names
  mutate(CARE_name_simple = fct_inorder(CARE_name_simple)) %>%
  # select only relevant columns
  select(ID,  moment, CARE_name_simple, CARE_value) %>%
  # summarise the data
  group_by(CARE_name_simple, CARE_value) %>%
  summarise(n = n()) %>%
  # calculate the proportion
  mutate(freq = n / sum(n)) %>% 
  select(-n) %>% 
  mutate(freq = freq * 100) %>% 
  pivot_wider(names_from = CARE_value, 
              values_from = freq, 
              values_fill = 0) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  relocate("Yes", .after = CARE_name_simple) %>% 
  relocate("Unclear", .after = "Yes")
```

### By raw scores

```{r}
df %>% 
  mutate(CARE_name_simple = fct_inorder(CARE_name_simple)) %>%
  select(ID,  moment, CARE_name_simple, CARE_value) %>%
  group_by(CARE_name_simple, CARE_value) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% 
  ggplot(aes(x = fct_rev(CARE_name_simple), 
             y = n, 
             fill = CARE_value)) + 
  geom_col(position = "fill") + 
  scale_fill_manual(values = c("#cc3232", "#e7b416", "#2dc937")) +
  coord_flip() + 
  labs(title = "CARE Items Compliance (Raw scores)", 
       x = "CARE Item", 
       y = "Percentage", 
       fill = "Compliance") +
  scale_y_continuous(labels = label_percent())
  
  
  
  

  
  
  
```

### By percentages

```{r}
df %>% 
  mutate(CARE_name_simple = fct_inorder(CARE_name_simple)) %>%
  select(ID,  moment, CARE_name_simple, CARE_value) %>%
  group_by(CARE_name_simple, CARE_value) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% 
  ggplot(aes(x = fct_rev(CARE_name_simple), 
             y = freq, 
             fill = CARE_value)) + 
  geom_col(position = "fill") + 
  scale_fill_manual(values = c("#cc3232", "#e7b416", "#2dc937")) +
  coord_flip() + 
  labs(title = "CARE Items Compliance (%)", 
       x = "CARE Item", 
       y = "Percentage", 
       fill = "Compliance") +
  scale_y_continuous(labels = label_percent())
```

## Change before and after

```{r}
df %>% 
  # reorder the CARE names
  mutate(CARE_name_simple = fct_inorder(CARE_name_simple)) %>%
  # select only relevant columns
  select(ID,  moment, CARE_name_simple, CARE_value) %>%
  # summarise the data
  group_by(CARE_name_simple, CARE_value, moment) %>%
  summarise(n = n()) %>%
  mutate(moment = fct_relevel(moment, c("Before", "After"))) %>% 
  mutate(CARE_value = fct_relevel(CARE_value, c("Yes", "Unclear", "No"))) %>% 
  pivot_wider(names_from = moment, 
              values_from = n, 
              values_fill = FALSE) %>% 
  mutate(suma = Before + After) %>% 
  mutate(Before = Before / suma * 100) %>% 
  mutate(After = After / suma * 100) %>% 
  ungroup() %>% 
  select(-c(suma)) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  filter(CARE_value == "Yes") %>% 
  
  # pivoting to long
  pivot_longer(Before:After, 
               names_to = "moment", 
               values_to = "moment_values") %>% 
  mutate(moment = fct_relevel(moment, c("Before"))) %>% 

  ggplot(aes(x = fct_rev(CARE_name_simple), 
             y = moment_values, 
             color = moment)) + 
  geom_point() + 
  coord_flip() +
  labs(title = "Change in percentage of compliance\n(CARE = Yes) before and after 2013", 
       x = "CARE Items", 
       y = "Compliance percentage", 
       color = "Moment")  +
  theme(legend.position="top")
  
  
  
  
  
  
```

```{r}
df %>%
  # reorder the CARE names
  mutate(CARE_name_simple = fct_inorder(CARE_name_simple)) %>%
  # select only relevant columns
  select(ID,  moment, CARE_name_simple, CARE_value) %>%
  # summarise the data
  group_by(CARE_name_simple, CARE_value, moment) %>%
  summarise(n = n()) %>%
  # calculate the proportion
  mutate(freq = n / sum(n)) %>%
  select(-n) %>%
  mutate(freq = freq * 100) %>%
  mutate(moment = fct_relevel(moment, c("Before"))) %>%
  filter(CARE_value == "Yes")  %>%
  ungroup() %>%
  select(-CARE_value) %>% 
  pivot_wider(names_from = moment, 
              values_from = freq, 
              values_fill = FALSE) %>% 
  relocate(Before, .after = CARE_name_simple) %>% 
  ggplot() +
  geom_segment(aes(
    x = fct_rev(CARE_name_simple),    xend = CARE_name_simple,
    y = Before,    yend = After  ), color = "grey") +
  
  geom_point(aes(x = CARE_name_simple, y = Before),
             color = "green", size = 3) +
  
  geom_point(aes(x = CARE_name_simple, y = After), 
             color = "red", size = 3) +  coord_flip() +
  coord_flip() + 
  labs(title = "Change in percentage of compliance\n(CARE = Yes) before and after 2013", 
       x = "CARE Items") 
  




```

# Wordcloud

```{r}

 docs <- Corpus(VectorSource(text))
```

```{r}
 docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
```

```{r}
# Convert the text to lower case
 docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
 docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
 docs <- tm_map(docs, removeWords, stopwords("english"))
# specify your stopwords as a character vector
 docs <- tm_map(docs, removeWords, c("keywords")) 
# Remove punctuations
 docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
 docs <- tm_map(docs, stripWhitespace)
# Text stemming
 docs <- tm_map(docs, stemDocument)
```

```{r}
 dtm <- TermDocumentMatrix(docs)
 m <- as.matrix(dtm)
 v <- sort(rowSums(m),decreasing=TRUE)
 d <- data.frame(word = names(v),freq=v)
 head(d, 10)
```

```{r}
 set.seed(1234)
 wordcloud(
  words = d$word,
  freq = d$freq,
  min.freq = 35,
  max.words = 200,
  random.order = TRUE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
 )
```

Which terms are correlated?

```{r}
# findAssocs(dtm, terms = "primary", corlimit = 0.3)
```

# Ingus 1 march 2022

I: Agreement between Ingus and Peteris

0.75

S: what is the quality of the reports?

I: what is the quality before and after 2013

I: difference between journals
